Thoughts on resubmission within ARC1

### 2009-03-16 doc/client/client_technical.tex
Adding documentation for arcmigrate

\documentclass{book}
%\documentclass{article}           %for shorter notes
\usepackage{graphicx}              %for PNG images (pdflatex)
%\usepackage{graphics}              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref}  %for \url tag
\usepackage{color}                 %for defining custom colors
\usepackage{framed}                %for shaded and framed paragraphs
\usepackage{textcomp}              %for various symbols, e.g. Registered Mark
\usepackage{geometry}              %for defining page size
\usepackage{longtable}             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {KnorARC collaboration},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\libarcclient}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Config}{\texttt{Config}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\RandomBroker}{\texttt{RandomBroker}}
\newcommand{\FastestCPUBroker}{\texttt{FastestCPUBroker}}
\newcommand{\FastestQueueBroker}{\texttt{FastestQueueBroker}}
\newcommand{\PythonBroker}{\texttt{PythonBroker}}
\newcommand{\DataBroker}{\texttt{DataBroker}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Sandbox}{\texttt{Sandbox}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

\begin{shaded}
\begin{verbatim}
void PreFilterTargets(Arc::TargetGenerator& targen, Arc::JobDescription jd);
\end{verbatim}
\end{shaded}

@@

\begin{shaded}
\begin{verbatim}
bool setSource(const std::string source);
\end{verbatim}
\end{shaded}

@@

\begin{shaded}
\begin{verbatim}
bool getProduct(std::string& product, std::string format = "POSIXJSDL")
\end{verbatim}
\end{shaded}

@@

\begin{shaded}
\begin{verbatim}
virtual bool Submit(JobDescription& jobdesc, XMLNode& info) = 0;
\end{verbatim}
\end{shaded}

@@

@@

\begin{shaded}
\begin{verbatim}
const std::list<Arc::JobController*>& GetJobControllers();
\end{verbatim}
\end{shaded}

@@

The other public functions of the {\JobController} class are:
The \texttt{Get} which is used to download jobs
\begin{shaded}
\begin{verbatim}
bool Get(const std::list<std::string>& status, const std::string& downloaddir,
         const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Kill(const std::list<std::string>& status, const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Clean(const std::list<std::string>& status, const bool force, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Cat(const std::list<std::string>& status, const std::string& whichfile, 
         const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool RemoveJobs(const std::list<URL>& jobids);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
std::list<std::string> GetDownloadFiles(const URL& dir);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool CopyFile(const URL& src, const URL& dst);
\end{verbatim}
\end{shaded}
The \texttt{GetJobDescriptions} method 
\begin{shaded}
\begin{verbatim}
std::list<Job> GetJobDescriptions(const std::list<std::string>& status, 
                                  const bool getlocal, const int timeout);
\end{verbatim}
\end{shaded}
which is used to get the job descriptions of {\Job}s in the \texttt{JobStore} 
with the specified status'. In case \texttt{getlocal} is true the job description 
will first be searched for the users local XML file. If a local copy of 
the job description is found the checksum of the local input files will be 
computed and compared with the ones listed in the users local XML file. If 
all checksums match the job description is returned.\\
In case \texttt{getlocal} is false or the retrieval of the local job description 
fails the job description will be tried retrieved from the cluster. This has 
currently only been implemented for ARC(both generations) clusters. Note 
that the job descriptions retried from a cluster might will most likely have 
been changed since the submission either by the cluster\footnote{For both 
generations of ARC it is possible to recover the initial job description send 
to the cluster. However modifications can still have been made to the 
job description before sending it to the cluster.} or by the submission 
client. Therefore the only way of retrieving the original job description is 
through the users local XML file.\\
The \texttt{GetJobDescriptions} returns a list of the  {\Job}s where job description 
have been found. The found job descriptions are kept in the 
{\Job}.\texttt{JobDescription} attribute.

>>>>

\documentclass{book}
%\documentclass{article}           %for shorter notes
\usepackage{graphicx}              %for PNG images (pdflatex)
%\usepackage{graphics}              %for EPS images (latex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref}  %for \url tag
\usepackage{color}                 %for defining custom colors
\usepackage{framed}                %for shaded and framed paragraphs
\usepackage{textcomp}              %for various symbols, e.g. Registered Mark
\usepackage{geometry}              %for defining page size
\usepackage{longtable}             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {KnowARC collaboration},
  pdftitle = {libarcclient},
  pdfsubject = {A Client Library for ARC},
  pdfkeywords = {ARC,client,library},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\globus}{Globus Toolkit\textsuperscript{\textregistered}~2~}
\newcommand{\GT}{Globus Toolkit\textsuperscript{\textregistered}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\newcommand{\libarcclient}{libarcclient}
\newcommand{\ACC}{\texttt{ACC}}
\newcommand{\ACCConfig}{\texttt{ACCConfig}}
\newcommand{\Config}{\texttt{Config}}
\newcommand{\Broker}{\texttt{Broker}}
\newcommand{\RandomBroker}{\texttt{RandomBroker}}
\newcommand{\FastestCPUBroker}{\texttt{FastestCPUBroker}}
\newcommand{\FastestQueueBroker}{\texttt{FastestQueueBroker}}
\newcommand{\PythonBroker}{\texttt{PythonBroker}}
\newcommand{\DataBroker}{\texttt{DataBroker}}
\newcommand{\ClientInterface}{\texttt{ClientInterface}}
\newcommand{\ClientTCP}{\texttt{ClientTCP}}
\newcommand{\ClientHTTP}{\texttt{ClientHTTP}}
\newcommand{\ClientSOAP}{\texttt{ClientSOAP}}
\newcommand{\ExecutionTarget}{\texttt{ExecutionTarget}}
\newcommand{\Job}{\texttt{Job}}
\newcommand{\JobController}{\texttt{JobController}}
\newcommand{\JobDescription}{\texttt{JobDescription}}
\newcommand{\JobSupervisor}{\texttt{JobSupervisor}}
\newcommand{\Loader}{\texttt{Loader}}
\newcommand{\Logger}{\texttt{Logger}}
\newcommand{\TargetGenerator}{\texttt{TargetGenerator}}
\newcommand{\TargetRetriever}{\texttt{TargetRetriever}}
\newcommand{\Sandbox}{\texttt{Sandbox}}
\newcommand{\Submitter}{\texttt{Submitter}}
\newcommand{\URL}{\texttt{URL}}
\newcommand{\UserConfig}{\texttt{UserConfig}}
\newcommand{\XML}{\texttt{XML}}
\newcommand{\XMLNode}{\texttt{XMLNode}}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

\begin{shaded}
\begin{verbatim}
void PreFilterTargets(const TargetGenerator& targen, const JobDescription& jd);
\end{verbatim}
\end{shaded}

@@

\begin{shaded}
\begin{verbatim}
bool setSource(const std::string source);
bool setSource(const XMLNode& source);
\end{verbatim}
\end{shaded}

@@

\begin{shaded}
\begin{verbatim}
bool getProduct(std::string& product, std::string format = "POSIXJSDL") const;
\end{verbatim}
\end{shaded}

@@

\begin{shaded}
\begin{verbatim}
virtual bool Submit(const JobDescription& jobdesc, XMLNode& info) const = 0;
\end{verbatim}
\end{shaded}

@@

\begin{shaded}
\begin{verbatim}
virtual bool Migrate(const URL& url,
                     const JobDescription& jobdesc,
                     bool forcemigration,
                     XMLNode& info) const = 0;
\end{verbatim}
\end{shaded}

The \texttt{Migrate} method behave in much the same way as the \texttt{Submit}
method, but is conceptually different from that method. The \texttt{Migrate}
method takes two additional arguments. A {\URL} \texttt{url} which is
the jobid of a job which should be migrated, and a boolean
\texttt{forcemigration} which will indicate if the job, specified in the
{\JobDescription} \texttt{jobdesc}, should persist if the cluster
({\ExecutionTarget}) does not succeed submitting a kill/terminate request
for the job specified by \texttt{url}. The \texttt{Migrate} method will
also fill the {\XMLNode} \texttt{info} variable with information about the
job for later job management, which additionally include the old jobid
(\texttt{url}) of the migrated job.

@@

\begin{shaded}
\begin{verbatim}
const std::list<JobController*>& GetJobControllers();
\end{verbatim}
\end{shaded}

@@

The other public methods of the {\JobController} class are:
The \texttt{Get} which is used to download jobs
\begin{shaded}
\begin{verbatim}
bool Get(const std::list<std::string>& status, const std::string& downloaddir,
         const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Kill(const std::list<std::string>& status, const bool keep, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Clean(const std::list<std::string>& status, const bool force, const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool Cat(const std::list<std::string>& status, const std::string& whichfile, 
         const int timeout);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool RemoveJobs(const std::list<URL>& jobids);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
std::list<std::string> GetDownloadFiles(const URL& dir);
\end{verbatim}
\end{shaded}
\begin{shaded}
\begin{verbatim}
bool CopyFile(const URL& src, const URL& dst);
\end{verbatim}
\end{shaded}
The \texttt{GetJobDescriptions} method 
\begin{shaded}
\begin{verbatim}
std::list<Job> GetJobDescriptions(const std::list<std::string>& status, 
                                  const bool getlocal, const int timeout);
\end{verbatim}
\end{shaded}
which is used to get the job descriptions of {\Job}s in the \texttt{JobStore} 
with the specified status'. In case \texttt{getlocal} is true the job description 
will first be searched for the users local XML file. If a local copy of 
the job description is found the checksum of the local input files will be 
computed and compared with the ones listed in the users local XML file. If 
all checksums match the job description is returned.\\
In case \texttt{getlocal} is false or the retrieval of the local job description 
fails the job description will be tried retrieved from the cluster. This has 
currently only been implemented for ARC(both generations) clusters. Note 
that the job descriptions retried from a cluster might will most likely have 
been changed since the submission either by the cluster\footnote{For both 
generations of ARC it is possible to recover the initial job description send 
to the cluster. However modifications can still have been made to the 
job description before sending it to the cluster.} or by the submission 
client. Therefore the only way of retrieving the original job description is 
through the users local XML file.\\
The \texttt{GetJobDescriptions} returns a list of the  {\Job}s where job description 
have been found. The found job descriptions are kept in the 
{\Job}.\texttt{JobDescription} attribute.

The \texttt{Migrate} method:
\begin{shaded}
\begin{verbatim}
bool Migrate(TargetGenerator& targetGen,
             Broker* broker,
             const bool forcemigration,
             const int timeout);
\end{verbatim}
\end{shaded}
will try to migrate the jobs contained in the object ({\JobController}). The jobs
will be migrated to the targets specified in {\TargetGenerator} \texttt{targetGen}
by using the broker specified by {\Broker} \texttt{broker}. The boolean
\texttt{forcemigration} specifies whether a migrated job should persist if the
new cluster ({\ExecutionTarget}) chosen by the {\TargetGenerator} does not
succeed submitting a kill/terminate request for the job. The integer
\texttt{timeout} argument have not yet been implemented.
